### 2014-01-24 Draft/background.tex
Fixed background

In particular, this work proposes novel techniques on top of previously proposed techniques~\cite{pandita12:inferring, pandita13:WHYPER} to demonstrate the effectiveness of applying NLP on API documents.
We next briefly introduce the techniques used in this work that have been grouped into broad categories.
We first introduce the core NLP techniques used in this work.
We then introduce the software engineering specific NLP techniques proposed in previous work~\cite{pandita12:inferring,pandita13:WHYPER} that have been used in this work.

@@

\textbf{Parts Of Speech (POS) tagging}~\cite{Klein03,KleinNIPS03}. Also known as \textit{`word tagging'}, \textit{`grammatical tagging'} and \textit{`word-sense disambiguation'}, these techniques aim to identify the part of speech (such as noun, verbs, etc.), a particular word in a sentence belongs to. The most commonly used technique is to train a classification parser over a previously known data set. Current state of the art approaches been have demonstrated to achieve 97\%~\cite{SNLP1} accuracy in classifying POS tags for well written news articles.

@@

\textbf{Named Entity Recognition}~\cite{Finkel05ACL}. Also known as \textit{`entity identification'} and \textit{`entity extraction'}, these techniques are a subtask of IE that aims to classify words in a sentence into predefined categories such as names, quantities, expression of times, etc. These techniques help in associating predefined semantic meaning to a word or a group of words (phrase), thus facilitating semantic processing of named entities.

@@

\textbf{Noun Boosting}~\cite{pandita12:inferring}. Accurate annotation of POS tags in a sentence is fundamental to effectiveness of any advanced NLP technique.
However, as mentioned earlier, POS tagging work well on well written news articles which does not necessary entail that the tagging works well on domain specific text as well.
Thus, noun boosting is a necessary precursor to application of POS tagging on domain specific text.
In particular, with respect to API documents certain words have a very different semantic meaning, in contrast to general linguistics that causes incorrect annotation of POS tags.

Consider the word \CodeIn{POST} for instance. 
The online Oxford dictionary~\footnote{\url{http://oxforddictionaries.com/us/definition/american_english/post?q=POST}} has 8 different definition of word \CodeIn{POST}, and none of them describes \CodeIn{POST} as a HTTP method
~\footnote{In HTTP vocabulary \CodeIn{POST} means: ''Creates a new entry in the collection.
The new entry's URI is assigned automatically and is usually returned by the operation''}
supported by REST API.
Thus existing POS tagging techniques fail to accurately annotate the POS tags of the sentences involving word \CodeIn{POST}.

Noun Boosting identifies such words from the sentences based on a domain-specific dictionaries, and annotates them appropriately.
The annotation assists the POS tagger to accurately annotate the POS tags of the words thus inturn increasing accuracy of advanced NLP techniques such as chunking and typed dependency annotation.

@@

\item \textbf{Abbreviation Handling}. Natural-language sentences often consist of abbreviations mixed with text.
This can result in subsequent components to incorrectly parse a sentence.
This heuristic finds such instances and annotates them as a single lexical unit.
For example, text followed by abbreviations such as \textit{``Access Control Lists (ACL)''} is treated as single lexical unit.
Detecting such abbreviations is achieved by using the common structure of abbreviations and encoding such structures into regular expressions.
Typically, regular expressions provide a reasonable approximation for handling abbreviations.

@@

\textbf{Intermediate-Representation Generation}~\cite{pandita13:WHYPER}.
This technique accepts the syntax-annotated sentences and builds a First-Order-Logic(FOL) representation of the sentence.
Earlier researches have shown the adequacy using FOL for NLP related analysis tasks~\cite{Sinha2009,Sinha2010,pandita12:inferring}.
In particular, WHYPER~\cite{pandita13:WHYPER} demonstrates the effectiveness of this technique, by constructing an intermediate representation generator based on shallow parsing~\cite{Branimir2000} techniques. 
The shallow parser itself is implemented as sequence of cascading finite state machines based on the functions of stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,Klein03,KleinNIPS03}.

>>>>

In particular, this work proposes novel techniques on top of previously proposed techniques~\cite{pandita12:inferring, pandita13:WHYPER} to demonstrate the effectiveness of applying NLP on API documents.
We next briefly introduce the techniques used in this work that have been grouped into broad categories.
We first introduce the core NLP techniques used in this work.
We then introduce the software engineering specific NLP techniques proposed in previous work~\cite{pandita12:inferring,pandita13:WHYPER} that are used in this work.

@@

\textbf{Parts Of Speech (POS) tagging}~\cite{Klein03,KleinNIPS03}. Also known as \textit{`word tagging'}, \textit{`grammatical tagging'} and \textit{`word-sense disambiguation'}, these techniques aim to identify the part of speech (such as noun, verbs, etc.), a particular word in a sentence belongs to. The most commonly used technique is to train a classification parser over a previously known data set. Current state of the art approaches have demonstrated to achieve 97\%~\cite{SNLP1} accuracy in classifying POS tags for well written news articles.

@@

\textbf{Named Entity Recognition}~\cite{Finkel05ACL}. Also known as \textit{`entity identification'} and \textit{`entity extraction'}, these techniques are a subtask of information extraction that aims to classify words in a sentence into predefined categories such as names, quantities, expression of times, etc. These techniques help in associating predefined semantic meaning to a word or a group of words (phrase), thus facilitating semantic processing of named entities.

@@

\textbf{Noun Boosting}~\cite{pandita12:inferring}. Accurate annotation of POS tags in a sentence is fundamental to effectiveness of any advanced NLP technique.
However, as mentioned earlier, POS tagging works well on well written news articles which does not necessary entail that the tagging works well on domain specific text as well.
Thus, noun boosting is a necessary precursor to application of POS tagging on domain specific text.
In particular, with respect to API documents certain words have a very different semantic meaning, in contrast to general linguistics that causes incorrect annotation of POS tags.

Consider the word \CodeIn{POST} for instance. 
The online Oxford dictionary\footnote{\url{http://oxforddictionaries.com/us/definition/american_english/post?q=POST}} has 8 different definition of word \CodeIn{POST}, and none of them describes \CodeIn{POST} as a HTTP method\footnote{In HTTP vocabulary \CodeIn{POST} means: ''Creates a new entry in the collection.
The new entry's URI is assigned automatically and is usually returned by the operation''}
supported by REST API.
Thus existing POS tagging techniques fail to accurately annotate the POS tags of the sentences involving word \CodeIn{POST}.

Noun Boosting identifies such words from the sentences based on a domain-specific dictionaries, and annotates them appropriately.
The annotation assists the POS tagger to accurately annotate the POS tags of the words thus in turn increasing accuracy of advanced NLP techniques such as chunking and typed dependency annotation.

@@

\item \textbf{Abbreviation Handling}. Natural-language sentences often consist of abbreviations mixed with text.
This phenomenon can result in subsequent components to incorrectly parse a sentence.
This heuristic finds such instances and annotates them as a single lexical unit.
For example, text followed by abbreviations such as \textit{``Access Control Lists (ACL)''} is treated as single lexical unit.
Detecting such abbreviations is achieved by using the common structure of abbreviations and encoding such structures into regular expressions.
Typically, regular expressions provide a reasonable approximation for handling abbreviations.

@@

\textbf{Intermediate-Representation Generation}~\cite{pandita13:WHYPER}.
This technique accepts the syntax-annotated sentences and builds a First-Order-Logic(FOL) representation of the sentence.
Earlier researches have shown the adequacy using FOL for NLP related analysis tasks~\cite{Sinha2009,Sinha2010,pandita12:inferring}.
In particular, WHYPER~\cite{pandita13:WHYPER} demonstrates the effectiveness of this technique, by constructing an intermediate representation generator based on shallow parsing~\cite{Branimir2000} techniques. 
The shallow parser itself is implemented as a sequence of cascading finite state machines based on the functions of stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,Klein03,KleinNIPS03}.
